Thinking...
We need to translate Japanese to English, preserving TeX code unchanged. The text includes references: 表\ref{tab:mostcitedA}, 表\ref{tab:mostcitedObs}, 図\ref{fig:nonobs}. Also "オブソレッセンス状態にあると判定されなかった". We need to produce English translation. Keep TeX code parts as they are: \ref{...}. Also preserve Japanese characters within TeX? No, only the code should be unchanged. So translate everything else. Provide proper English academic style.

Let's craft translation:

"Furthermore, none of the most cited papers shown in Table \ref{tab:mostcitedA} were judged to be in an obsolescence state. For these three papers, the values of each metric are listed in Table \ref{tab:mostcitedObs}, and the yearly citation counts are plotted in Figure \ref{fig:nonobs}. All of the papers have a very long period from publication to their citation peak, and they continue to receive a substantial number of citations each year. For two of the papers, a multimodal pattern can be observed, and their citation trends are similar."

Check: "オブソレッセンス状態にあると判定されなかった" -> "were not judged to be in an obsolescence state". Could phrase as "were not classified as being in an obsolescence state." We'll choose.

Make sure to keep TeX code unchanged, i.e., \ref{tab:mostcitedA} etc. The rest is English. Provide translation as a paragraph.
...done thinking.

Furthermore, none of the most‑cited papers shown in Table \ref{tab:mostcitedA} were classified as being in an obsolescence state. For these three papers, the values of each metric are presented in Table \ref{tab:mostcitedObs}, and the year‑by‑year citation counts are plotted in Figure \ref{fig:nonobs}. All of the papers have a very long interval from publication to their citation peak, and they continue to receive a substantial number of citations each year. In two of the papers a multimodal pattern can be observed, and their citation trends are similarly shaped.

