Thinking...
The user wants translation of Japanese text to English, preserving TeX code parts as is. Need to output English translation with TeX code unchanged. Provide translation.

Let's translate:

"以上より、高被引用論文には次の特徴があると考えられる：(1)高被引用論文は異なるテーマから引用されやすい。このことは表6の最頻出テーマから予想され、図\ref{fig:meshpivot}に示す転換の程度もこれを裏付けている。(2)高被引用論文は研究テーマが集中的であり、それを引用する論文の研究テーマもまた集中的である。このことは図\ref{fig:arr2}から示唆される。(3)高被引用論文のテーマの多様性は、共時的には低いが通時的には必ずしも低くないと思われる。このことは、図17では他のグループに比べ低いエントロピーが観察されるにもかかわらず、図\ref{fig:gr15}では他のグループと変わらない程度の転換が観察されることから推察される。"

English translation:

"From the above, we can consider that highly cited papers have the following characteristics: (1) Highly cited papers tend to be cited from different topics. This can be inferred from the most frequent topics in Table 6, and the degree of pivot shown in Figure \ref{fig:meshpivot} also supports this. (2) Highly cited papers have concentrated research topics, and the papers that cite them also have concentrated research topics. This is suggested by Figure \ref{fig:arr2}. (3) The thematic diversity of highly cited papers is low synchronically but not necessarily low diachronically. This is inferred from the fact that, although Figure 17 shows lower entropy compared with other groups, Figure \ref{fig:gr15} shows a level of pivot comparable to other groups."

Make sure TeX code unchanged: \ref{fig:meshpivot}, etc. Also Table 6 maybe keep as Table 6 (or 表6). They said TeX code only; Table 6 is not TeX, fine.

Let's output final.
...done thinking.

From the above, we can infer that highly cited papers have the following characteristics: (1) Highly cited papers tend to be cited from different topics. This can be anticipated from the most frequent topics shown in Table 6, and the degree of pivot displayed in Figure \ref{fig:meshpivot} also supports this. (2) Highly cited papers have concentrated research topics, and the papers that cite them likewise have concentrated research topics. This is suggested by Figure \ref{fig:arr2}. (3) The thematic diversity of highly cited papers is low synchronically but not necessarily low diachronically. This is inferred from the fact that, although Figure 17 shows lower entropy compared with other groups, Figure \ref{fig:gr15} exhibits a level of pivot comparable to that of other groups.

