Thinking...
We need to translate Japanese to English, preserving TeX code as is. Provide translation. Ensure TeX parts unchanged: figure reference \ref{fig:gr15}. Also "被引用テーマ" etc remain Japanese? Should we keep them? Probably keep as is because they are terms. We'll translate whole sentence, keep TeX code.

Let's produce translation:

"Furthermore, to assess the degree of shift in cited topics between each cumulative generation, we observed the cosine distance of cited topics between cumulative generations for each group. Since the members of the paper set differ between cumulative generations, we used the weighted count of topics for the entire paper set. The results are shown in Figure \ref{fig:gr15}. According to this, the degree of shift in cited topics between cumulative generations did not exhibit a consistent trend, but only Group 2 consistently maintained a low degree of shift."

Make sure preserve TeX code.

Provide final.
...done thinking.

Furthermore, to assess the degree of shift in cited topics between each cumulative generation, we observed the cosine distance of cited topics between the cumulative generations for each group. Because the members of the paper set differ across cumulative generations, we used the weighted‑count of topics for the entire paper set. The results are shown in Figure \ref{fig:gr15}. According to this, the degree of shift in cited topics between cumulative generations did not exhibit a consistent trend, but only Group 2 consistently maintained a low degree of shift.

