Thinking...
We need to translate Japanese text to English, preserving TeX code unchanged. The Japanese text: "以下のの日本語文を英訳してください。ただしTeXのコードが挿入されているのでその部分はそのまま出力してください：" Then the TeX code is a table. We need to translate the surrounding Japanese instructions? Probably we output the English translation of the Japanese description (the caption etc.)? Actually the Japanese sentence to translate includes the whole snippet? The snippet contains Japanese in caption and labels etc. Need to translate Japanese parts within TeX: caption, maybe label? The table content includes Japanese? The rows are years, and "G1引用テーマ", "被引用テーマ", etc. These are Japanese column headers. Need to translate them to English while keeping TeX structure. So we replace Japanese text with English equivalents, preserving code.

Thus output should be same TeX code but with English translations: caption: "Most Frequent Topics by Paper Group for Each Cumulative Generation" maybe. label unchanged. Within array: leftmost column years (numbers) okay. Then column headers: "G1引用テーマ" => "G1 Cited Theme"? Actually "引用テーマ" = "citing theme"? "被引用テーマ" = "cited theme". Could be "Citing Theme" and "Cited Theme". So header pair maybe "G1 Citing Theme" & "Cited Theme". But each column shows two subcolumns: first is "G1引用テーマ" and second is "被引用テーマ". So we translate to "G1 Citing Theme" and "Cited Theme". Similarly for G2, G3, G4.

Also maybe translate "累積世代ごと論文グループごとの最頻出テーマ" to "Most Frequent Themes by Paper Group for Each Cumulative Generation". Use that.

Thus produce TeX with same structure, just replace Japanese strings.

Let's craft final output.
...done thinking.

\begin{table*}[h]
\begin{center}
\caption{Most Frequent Themes by Paper Group for Each Cumulative Generation}
\label{tab:topmesh}
{\tiny
\[
\begin{array}{c|cccc}
\begin{array}{c}
{ } \\
\hline
{1946-1955} \\
{1946-1960} \\
{1946-1965} \\
{1946-1970} \\
{1946-1975} \\
{1946-1980} \\
{1946-1985} \\
{1946-1990} \\
{1946-1995} \\
{1946-2000} \\
{1946-2005} \\
{1946-2010} \\
{1946-2015} \\
{1946-2020} \\
\end{array}
&
\begin{array}{cc}
{G1 Citing Theme} & {Cited Theme} \\
\hline
{Humans} & {Insulin} \\
{Humans} & {Blood Proteins} \\
{Animals} & {Microscopy, Electron} \\
{Animals} & {Microscopy, Electron} \\
{Animals} & {Microscopy, Electron} \\
{Animals} & {Proteins} \\
{Animals} & {Proteins} \\
{Animals} & {Proteins} \\
{Animals} & {Base Sequence} \\
{Animals} & {Base Sequence} \\
{Animals} & {Base Sequence} \\
{Animals} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
\end{array}
&
\begin{array}{cc}
{G2 Citing Theme} & {Cited Theme} \\
\hline
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Animals} & {Humans} \\
{Animals} & {Animals} \\
{Animals} & {Humans} \\
{Animals} & {Animals} \\
{Humans} & {Animals} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
\end{array}
&
\begin{array}{cc}
{G3 Citing Theme} & {Cited Theme} \\
\hline
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Animals} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
\end{array}
&
\begin{array}{cc}
{G4 Citing Theme} & {Cited Theme} \\
\hline
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Animals} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
{Humans} & {Humans} \\
\end{array}
\\
\end{array}
\]
}
\end{center}
\end{table*}

